---
title: "asr_fit_example"
author: "Jeff Miller"
date: "6/30/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Example of fitting ASR to experimental data

This file gives a small example of how you might write code
to fit the ASR model to your observed RT data.

## Setup

First load the necessary packages and functions so that R will recognize the toolkit functions:

```{r initialize, include=TRUE, results='hide', warning=FALSE}
library(gamlss, quietly = TRUE)
library(pracma)

source("asr_fit.R")
source("asr_distribution.R")
source("asr_predictions.R")
```

## Load some example data

We need some data to illustrate the fitting process.
Of course you would load your own data here.

```{r load}
test_data_df <- read.csv("asr_sample_data.csv", header = TRUE)
head(test_data_df)
```

## Fit the model

The function asr_fit does all the work of fitting the ASR model (i.e. estimate model parameters) to a given
set of congruent and incongruent RTs.

You have to write code to (a) select out the appropriate RTs for each subject, condition, etc, and (b) save the fitted parameter values.

For this illustration, only two subjects are fit in the interests of speed:

```{r fitting}
# Initialise soa based on the experimental design from which
# the data are derived
soa <- 0

# Make an empty data frame to hold the parameter estimates for all participants
allBest = data.frame()
 
for (iSub in c(2,3)) {
  
  # Fit each subject individually.
  # paste("fitting subject",iSub)
  
  # First, select the congruent & incongruent RTs for this subject.
  # You probably also want to exclude errors & outlier RTs,
  # but that is not illustrated.
  # If you have an experimental factor (e.g. SOA) such that there are 
  # multiple congruent/incongruent pairs per subject, then you would
  # fit each pair separately.
  obsRTcon <- test_data_df$RT[test_data_df$SubNo == iSub
                              & test_data_df$Congru == 1]
  
  obsRTinc <- test_data_df$RT[test_data_df$SubNo == iSub
                              & test_data_df$Congru==2]
  
  # Function asr_fit finds the maximum likelihood estimates of the model 
  # parameters and stores them in the BestParameters field of the output.
  # By default, asr_fit assumes that lambda_exc is fixed at 0.
  # For explanation of the other outputs in fixed_exc, check the
  # comments in the asr_fit function.
  fixed_exc <- asr_fit(obsRTcon,obsRTinc,soa,display_params = FALSE)
  
  # Now extract the parameters for this subject from fixed_exc, add the subject ID,
  # and save the results as a new row in the allBest data_frame.
  currentRow <- fixed_exc$BestParameters
  currentRow <- c(SubNo = iSub,currentRow, BestError = fixed_exc$MinError)
  allBest <- rbind(allBest,currentRow)
}
```
## Look at the results

The allBest data frame now has the best parameter estimates for all subjects:
```{r}
allBest
```
These parameter values could then be compared between groups or conditions using standard statistical techniques (e.g., t-tests, ANOVAs), in essentially the same way as other RT results could be compared (e.g., condition mean RTs, parameters of ex-Gaussian or other model fits).
